Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
typo in abstract

\begin{abstract}
%
We present a sound and automated approach to synthesize safe digital
feedback controllers for physical plants represented as linear, time
invariant models.  Models are described as dynamical equations with inputs,
evolving over a continuous state space and accounting for errors due to the
digitalization of signals by the controller.  The approach works in two
stages, leveraging counterexample guided inductive synthesis (CEGIS) and
reachability analysis.  CEGIS synthesises a static feedback controller that
stabilizes the system under some restrictions given by the safety of the
reach space.  Safety is verfied iether via BMC or abstract acceleration; if
the verification step fails, we generate an alternative controller by
generalizing the counterexample.  We synthesize stable and safe controllers
for intricate physical plant models from the digital control literature.
%
\keywords{
State-space dynamical models of physical systems; 
Digital controllers; 
Analogue-to-digital converters; 
Time sampling; 
quantization; 
Fixed-point arithmetic; 
CEGIS; 
safety requirements. 
}
\end{abstract}

>>>>

\begin{abstract}
%
We present a sound and automated approach to synthesize safe digital
feedback controllers for physical plants represented as linear, time
invariant models.  Models are described as dynamical equations with inputs,
evolving over a continuous state space and accounting for errors due to the
digitalization of signals by the controller.  The approach works in two
stages, leveraging counterexample guided inductive synthesis (CEGIS) and
reachability analysis.  CEGIS synthesises a static feedback controller that
stabilizes the system under some restrictions given by the safety of the
reach space.  Safety is verified either via BMC or abstract acceleration; if
the verification step fails, we generate an alternative controller by
generalizing the counterexample.  We synthesize stable and safe controllers
for intricate physical plant models from the digital control literature.
%
\keywords{
State-space dynamical models of physical systems; 
Digital controllers; 
Analogue-to-digital converters; 
Time sampling; 
quantization; 
Fixed-point arithmetic; 
CEGIS; 
safety requirements. 
}
\end{abstract}
